Visit Scotland Notebook

### 2023-06-16 draft_work.Rmd
Added Tourism Businesses Dataset / Tidied Cleaning Script

>>>>

```{r}
# Clean Activities Data ------------------------------------------------------------

# activities_clean <- activities %>%
#   filter(tourism_activity != "All") %>% 
#   select(-c(measurement, units)) %>%
#   arrange(date_code) %>% 
#   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>% 
#   mutate(exp_per_visit = Expenditure / Visits,
#          tourism_activity = recode(tourism_activity,
#                                    "Day out to a beauty/health centre/spa, etc." = "Beauty/Health Centre/Spa",
#                                    "Day trips/excursions for other leisure purpose" = "Day Trips for Other Leisure Purpose",
#                                    "Entertainment - to a cinema, concert or theatre	" = "Entertainment (eg. Cinema, Concert)",
#                                    "General day out/ to explore an area" = "General Day Out / Explore an Area",
#                                    "Leisure activities e.g. hobbies & evening classes" = "Leisure Activities (eg. Hobbies)",
#                                    "Night out to a bar, pub and/or club" = "Night Out (eg. Bar, Pub)",
#                                    "Outdoor leisure activities e.g. walking, golf" = "Outdoor Leisure (eg. Golf)",
#                                    "Shopping for items that you do not regularly buy" = "Shopping for Non-Regular Purchases",
#                                    "Special personal events e.g. wedding, graduation" = "Special Personal Event (eg. Wedding)",
#                                    "Special public event e.g. festival, exhibition" = "Special Public Event (eg. Festival)",
#                                    "Sport participation, e.g. exercise classes, gym" = "Sport Participation",
#                                    "Visited friends or family for leisure	" = "Visiting Friends/Family for Leisure",
#                                    "Visitor attraction e.g. theme park, museum, zoo" = "Visitor Attraction (eg. Museum)",
#                                    "Watched live sporting events (not on TV)" = "Attending Sporting Event",
#                                    "Went out for a meal" = "Eating Out")) %>% 
#   rename(year = date_code) %>% 
#   clean_names()

# Clean Demographic Data ------------------------------------------------------------

# all_demographics_clean <- demographics %>%
#   filter(age == "All", marital_status == "All", gender == "All", employment_status == "All",
#          children == "All",  access_to_car == "All", social_grade == "All") %>%
#   select(-c(measurement, units)) %>% 
#   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>%
#   arrange(date_code) %>% 
#   mutate(exp_per_visit = Expenditure / Visits,
#          exp_per_visit_pct_change = (exp_per_visit - lag(exp_per_visit)) / lag(exp_per_visit) * 100,
#          visits_change_label = case_when(Visits > lag(Visits) ~ "Increased",
#                                          Visits < lag(Visits) ~ "Decreased",
#                                          Visits == lag(Visits) ~ "No Change",
#                                          TRUE ~ "Starting Year"),
#          exp_change_label = case_when(Expenditure > lag(Expenditure) ~ "Increased",
#                                       Expenditure < lag(Expenditure) ~ "Decreased",
#                                       Expenditure == lag(Expenditure) ~ "No Change",
#                                       TRUE ~ "Starting Year"),
#          exp_per_visit_label = case_when(exp_per_visit > lag(exp_per_visit) ~ "Increased",
#                                          exp_per_visit < lag(exp_per_visit) ~ "Decreased",
#                                          exp_per_visit == lag(exp_per_visit) ~ "No Change",
#                                          TRUE ~ "Starting Year")) %>% 
#   select(date_code, Visits, Expenditure, exp_per_visit, exp_per_visit_pct_change, 
#          visits_change_label, exp_change_label, exp_per_visit_label) %>% 
#   rename(year = date_code) %>% 
#   clean_names()
# 
# employment_demographics_clean <- demographics %>%
#   select(-c(feature_code, age, marital_status, gender, children, access_to_car, 
#             social_grade, measurement, units)) %>% 
#   filter(employment_status != "All") %>% 
#   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>%
#   arrange(date_code) %>% 
#   mutate(exp_per_visit = Expenditure / Visits) %>% 
#   select(date_code, employment_status, Visits, Expenditure, exp_per_visit) %>% 
#   rename(year = date_code) %>% 
#   clean_names()
# 
# gender_demographics_clean <- demographics %>%
#   select(-c(feature_code, age, marital_status, children, access_to_car, 
#             social_grade, measurement, units, employment_status)) %>% 
#   filter(gender != "All") %>% 
#   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>%
#   arrange(date_code) %>% 
#   mutate(exp_per_visit = Expenditure / Visits) %>% 
#   select(date_code, gender, Visits, Expenditure, exp_per_visit) %>% 
#   rename(year = date_code) %>% 
#   clean_names()
# 
# age_demographics_clean <- demographics %>%
#   select(-c(feature_code, gender, marital_status, children, access_to_car, 
#             social_grade, measurement, units, employment_status)) %>% 
#   filter(age != "All") %>% 
#   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>%
#   arrange(date_code) %>% 
#   mutate(exp_per_visit = Expenditure / Visits) %>% 
#   select(date_code, age, Visits, Expenditure, exp_per_visit) %>% 
#   rename(year = date_code) %>% 
#   clean_names()
# 
# marital_status_demographics_clean <- demographics %>%
#   select(-c(feature_code, gender, age, children, access_to_car, 
#             social_grade, measurement, units, employment_status)) %>% 
#   filter(marital_status != "All") %>% 
#   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>%
#   arrange(date_code) %>% 
#   mutate(exp_per_visit = Expenditure / Visits) %>% 
#   select(date_code, marital_status, Visits, Expenditure, exp_per_visit) %>% 
#   rename(year = date_code) %>% 
#   clean_names()
# 
# children_demographics_clean <- demographics %>%
#   select(-c(feature_code, gender, age, marital_status, access_to_car, 
#             social_grade, measurement, units, employment_status)) %>% 
#   filter(children != "All") %>% 
#   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>%
#   arrange(date_code) %>% 
#   mutate(exp_per_visit = Expenditure / Visits) %>% 
#   select(date_code, children, Visits, Expenditure, exp_per_visit) %>% 
#   rename(year = date_code) %>% 
#   clean_names()
# 
# car_demographics_clean <- demographics %>%
#   select(-c(feature_code, gender, age, marital_status, children, 
#             social_grade, measurement, units, employment_status)) %>% 
#   filter(access_to_car != "All") %>% 
#   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>%
#   arrange(date_code) %>% 
#   mutate(exp_per_visit = Expenditure / Visits) %>% 
#   select(date_code, access_to_car, Visits, Expenditure, exp_per_visit) %>% 
#   rename(year = date_code) %>% 
#   clean_names()
# 
# social_demographics_clean <- demographics %>%
#   select(-c(feature_code, gender, age, marital_status, children, 
#             access_to_car, measurement, units, employment_status)) %>% 
#   filter(social_grade != "All") %>% 
#   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>%
#   arrange(date_code, social_grade) %>% 
#   mutate(exp_per_visit = Expenditure / Visits) %>% 
#   select(date_code, social_grade, Visits, Expenditure, exp_per_visit) %>% 
#   rename(year = date_code) %>% 
#   clean_names()

```{r}
tourism_businesses %>%
  filter(local_authority != "Scotland",
         year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>%
  group_by(local_authority) %>% 
  summarise(mean_gva = mean(gva),
            total_gva = sum(gva)) %>% 
  arrange(desc(mean_gva))

```{r}
tourism_businesses %>%
  filter(local_authority == "Scotland",
         year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>%
  group_by(local_authority) %>% 
  summarise(mean_gva = mean(gva),
            total_gva = sum(gva))
```

### 2023-06-16 visit_scotland_notebook.Rmd
Added Tourism Businesses Dataset / Tidied Cleaning Script

regional_domestic_tourism_all <- read_csv(here("data/clean_data/regional_domestic_tourism_all_clean.csv"))
regional_domestic_tourism_individual <- read_csv(here("data/clean_data/regional_domestic_tourism_individual_clean.csv"))
regional_domestic_tourism_non_gb_clean <- read_csv(here("data/clean_data/regional_domestic_tourism_non_gb_clean.csv"))
international_visits <- read_csv(here("data/clean_data/international_visits_clean.csv"))
local_authority_geo <- st_read(dsn = "data/geo_data/", layer = "pub_las")

@@

```{r}
international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>% 
  group_by(country) %>% 
  summarise(total_visits = sum(visits)) %>%
  slice_max(total_visits, n = 20) %>% 
  ggplot(aes(x = reorder(country, total_visits), y = total_visits)) +
  geom_col(aes(x = reorder(country, total_visits), y = total_visits,
               fill = country %in% c("USA")),
           show.legend = FALSE, colour = "white") +
  scale_fill_manual(values = c("FALSE" = "grey60",
                               "TRUE" = "#540453")) +
  coord_flip() +
  labs(
    x = "Country",
    y = "Total Visits (Thousands)",
    title = "International Tourism: Total Visits (2002-2009)",
    subtitle = "Top 20")
```

@@

```{r}
international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>% 
  group_by(country) %>% 
  summarise(total_spend = sum(spend)) %>%
  slice_max(total_spend, n = 20) %>% 
  ggplot() +
  geom_col(aes(x = reorder(country, total_spend), y = total_spend,
               fill = country %in% c("USA")),
           show.legend = FALSE, colour = "white") +
  scale_fill_manual(values = c("FALSE" = "grey60",
                               "TRUE" = "#540453")) +
  coord_flip() +
  labs(
    x = "Country",
    y = "Total Spend (Million GBP)",
    title = "International Tourism: Total Spend (2002-2009)",
    subtitle = "Top 20")
```

@@

```{r}
international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>% 
  group_by(country) %>% 
  summarise(total_spend = sum(spend),
            total_visits = sum(visits),
            spend_per_visit = total_spend / total_visits) %>%
  filter(total_visits > 500) %>%
  ggplot() +
  geom_col(aes(x = reorder(country, spend_per_visit), y = spend_per_visit,
               fill = country %in% c("Australia", "China", "Canada", "Switzerland")),
           show.legend = FALSE, colour = "white") +
  scale_fill_manual(values = c("FALSE" = "grey60",
                               "TRUE" = "#540453")) +
  coord_flip() +
  labs(
    x = "Country",
    y = "Total Spend (Million GBP) / Visit (Thousands)",
    title = "International Tourism: Total Spend per Visit (2002-2009)",
    subtitle = "Countries w/ Over 500 Thousand Total Visits")
```

@@

```{r}
international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>% 
  group_by(country) %>% 
  summarise(total_spend = sum(spend),
            total_visits = sum(visits),
            spend_per_visit = total_spend / total_visits) %>%
  filter(total_visits > 500) %>% 
  ggplot(aes(x = total_visits, y = spend_per_visit)) +
  geom_point(aes(colour = country %in% c("Australia", "China", "Canada", "Switzerland")), 
             show.legend = FALSE,
             size = 4) +
  scale_colour_manual(values = c("FALSE" = "grey60",
                                 "TRUE" = "#970061")) +
  ggrepel::geom_text_repel(aes(x = total_visits, y = spend_per_visit, label = country)) +
  labs(
    x = "Visits (Thousands)",
    y = "Total Spend (Million GBP) / Visit (Thousands)",
    title = "International Tourism: Visits vs. Spend Per Visit (2002-2009)",
    subtitle = "Countries w/ Over 500 Thousand Total Visits")
```

@@

```{r}
international_visits %>%
  filter(country == "Canada") %>% 
  mutate(exp_per_visit = spend / visits,
         spring_summer = if_else(quarter %in% c("Quarter 2", "Quarter 3"), "Yes", "No")) %>%  group_by(spring_summer) %>% 
  summarise(mean_visits = mean(visits),
            mean_exp = mean(spend),
            mean_exp_per_visit = mean(exp_per_visit))
```
```{r}
canada_sample <- international_visits %>%
  filter(country == "Canada") %>% 
  mutate(exp_per_visit = spend / visits,
         spring_summer = if_else(quarter %in% c("Quarter 2", "Quarter 3"), "Yes", "No"))
```

>>>>

regional_domestic_tourism_all <- read_csv(here("data/clean_data/regional_domestic_tourism_all_clean.csv"))
regional_domestic_tourism_individual <- read_csv(here("data/clean_data/regional_domestic_tourism_individual_clean.csv"))
regional_domestic_tourism_non_gb_clean <- read_csv(here("data/clean_data/regional_domestic_tourism_non_gb_clean.csv"))
international_visits <- read_csv(here("data/clean_data/international_visits_clean.csv"))
tourism_businesses <- read_csv(here("data/clean_data/tourism_businesses_clean.csv"))
local_authority_geo <- st_read(dsn = "data/geo_data/", layer = "pub_las")

@@

```{r}
international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019),
         purpose == "Holiday") %>% 
  group_by(country) %>% 
  summarise(total_visits = sum(visits)) %>%
  slice_max(total_visits, n = 20) %>% 
  ggplot(aes(x = reorder(country, total_visits), y = total_visits)) +
  geom_col(aes(x = reorder(country, total_visits), y = total_visits,
               fill = country %in% c("USA")),
           show.legend = FALSE, colour = "white") +
  scale_fill_manual(values = c("FALSE" = "grey60",
                               "TRUE" = "#540453")) +
  coord_flip() +
  labs(
    x = "Country",
    y = "Total Visits (Thousands)",
    title = "International Tourism: Total Visits (2002-2009)",
    subtitle = "Top 20 (Holiday Only)")
```

@@

```{r}
international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019),
         purpose == "Holiday") %>% 
  group_by(country) %>% 
  summarise(total_spend = sum(spend)) %>%
  slice_max(total_spend, n = 20) %>% 
  ggplot() +
  geom_col(aes(x = reorder(country, total_spend), y = total_spend,
               fill = country %in% c("USA")),
           show.legend = FALSE, colour = "white") +
  scale_fill_manual(values = c("FALSE" = "grey60",
                               "TRUE" = "#540453")) +
  coord_flip() +
  labs(
    x = "Country",
    y = "Total Spend (Million GBP)",
    title = "International Tourism: Total Spend (2002-2009)",
    subtitle = "Top 20 (Holiday Only)")
```

@@

```{r}
international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019),
         purpose == "Holiday") %>% 
  group_by(country) %>% 
  summarise(total_spend = sum(spend),
            total_visits = sum(visits),
            spend_per_visit = total_spend / total_visits) %>%
  filter(total_visits > 500) %>%
  ggplot() +
  geom_col(aes(x = reorder(country, spend_per_visit), y = spend_per_visit,
               fill = country %in% c("Australia", "China", "Canada")),
           show.legend = FALSE, colour = "white") +
  scale_fill_manual(values = c("FALSE" = "grey60",
                               "TRUE" = "#540453")) +
  coord_flip() +
  labs(
    x = "Country",
    y = "Total Spend (Million GBP) / Visit (Thousands)",
    title = "International Tourism: Total Spend per Visit (2002-2009)",
    subtitle = "Countries w/ Over 500 Thousand Total Visits (Holiday Only)")
```

@@

```{r}
international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019),
         purpose == "Holiday") %>% 
  group_by(country) %>% 
  summarise(total_spend = sum(spend),
            total_visits = sum(visits),
            spend_per_visit = total_spend / total_visits) %>%
  filter(total_visits > 500) %>% 
  ggplot(aes(x = total_visits, y = spend_per_visit)) +
  geom_point(aes(colour = country %in% c("Australia", "China", "Canada")), 
             show.legend = FALSE,
             size = 4) +
  scale_colour_manual(values = c("FALSE" = "grey60",
                                 "TRUE" = "#970061")) +
  ggrepel::geom_text_repel(aes(x = total_visits, y = spend_per_visit, label = country)) +
  labs(
    x = "Visits (Thousands)",
    y = "Total Spend (Million GBP) / Visit (Thousands)",
    title = "International Tourism: Visits vs. Spend Per Visit (2002-2009)",
    subtitle = "Countries w/ Over 500 Thousand Total Visits (Holiday Only)")
```

@@

```{r}
international_visits %>%
  filter(country == "Canada",
         purpose == "Holiday") %>% 
  mutate(exp_per_visit = spend / visits,
         spring_summer = if_else(quarter %in% c("Quarter 2", "Quarter 3"), "Yes", "No")) %>%  group_by(spring_summer) %>% 
  summarise(mean_visits = mean(visits),
            mean_exp = mean(spend),
            mean_exp_per_visit = mean(exp_per_visit))
```
```{r}
canada_sample <- international_visits %>%
  filter(country == "Canada",
         purpose == "Holiday") %>% 
  mutate(exp_per_visit = spend / visits,
         spring_summer = if_else(quarter %in% c("Quarter 2", "Quarter 3"), "Yes", "No"))
```
